Different forms of uncertainty differently affect the evolution of social learning

### 2022-07-30 meanNetPayoffs.tex
updated main analysis figures to all be N=1000

    \begin{minipage}{3.75in}
      \centering
      {\hspace{5.25em}\huge $B = 4$}
    \end{minipage}%
    \begin{minipage}{3.75in}
      \centering
      {\hspace{2.0em}\huge $B = 10$}
    \end{minipage}~\\

    \begin{minipage}{3.75in}
    \begin{rotate}{90}
      {\parbox{2.5in}{
          \centering
          \vspace{-2.5em} {\huge$ \pilow = 0.1$} \\
          {\begin{rotate}{-90}{\huge $\frac{\meanpi}{L}$}\hspace{3em}\end{rotate}}
      }}
    \end{rotate}%
    \hspace{2em}
      \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.1_nbehaviors=4.pdf}
    \end{minipage}\noindent\begin{minipage}{3.75in}%
      \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.1_nbehaviors=10.pdf}
    \end{minipage}~\\[0.5em]

    \begin{minipage}{3.75in}
    \begin{rotate}{90}
      {\parbox{2.5in}{
          \centering
          \vspace{-2.5em} {\huge$ \pilow = 0.45$} \\
          {\begin{rotate}{-90}{\huge $\frac{\meanpi}{L}$}\hspace{3em}\end{rotate}}
      }}
    \end{rotate}%
    \hspace{2em}
      \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.45_nbehaviors=4.pdf}
        \\[-2.75em]
        \begin{center}
          {\hspace{3.25em} \huge $\quad u$}
      \end{center}
        \end{minipage}\noindent\begin{minipage}{3.75in}%
      \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.45_nbehaviors=10.pdf}
      \\[-2.75em]
      \begin{center}
        {\huge $\quad u$}
      \end{center}
    \end{minipage}
\end{document}

>>>>

    \begin{minipage}{3.75in}
      \centering
      {\hspace{5.25em}\huge $B = 2$}
    \end{minipage}%
    \begin{minipage}{3.75in}
      \centering
      {\hspace{2.0em}\huge $B = 10$}
    \end{minipage}~\\

    \begin{minipage}{3.75in}
    \begin{rotate}{90}
      {\parbox{2.5in}{
          \centering
          \vspace{-2.5em} {\huge$ \pilow = 0.1$} \\
          {\begin{rotate}{-90}{\huge $\frac{\meanpi}{L}$}\hspace{3em}\end{rotate}}
      }}
    \end{rotate}%
    \hspace{2em}
      \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.1_nbehaviors=2.pdf}
    \end{minipage}\noindent\begin{minipage}{3.75in}%
      \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.1_nbehaviors=10.pdf}
    \end{minipage}~\\[0.5em]

    \begin{minipage}{3.75in}
    \begin{rotate}{90}
      {\parbox{2.5in}{
          \centering
          \vspace{-2.5em} {\huge$ \pilow = 0.45$} \\
          {\begin{rotate}{-90}{\huge $\frac{\meanpi}{L}$}\hspace{3em}\end{rotate}}
      }}
    \end{rotate}%
    \hspace{2em}
      \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.45_nbehaviors=2.pdf}
        \\[-2.75em]
        \begin{center}
          {\hspace{3.25em} \huge $\quad u$}
      \end{center}
        \end{minipage}\noindent\begin{minipage}{3.75in}%
      \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.45_nbehaviors=10.pdf}
      \\[-2.75em]
      \begin{center}
        {\huge $\quad u$}
      \end{center}
    \end{minipage}
\end{document}

### 2022-07-30 ms.tex
updated main analysis figures to all be N=1000

\mt{Need to make this section more specific in reviewing the findings.} By
systematizing four common uncertainty dimensions we developed a model of the
evolution of social learning that predicts how different forms of uncertainty might
interact to foster or suppress social learning.  The model reproduced classic
predictions that social learning can yield higher payoffs than individual learning
when uncertainty is sufficiently limited.  
% By disambiguating and organizing various
% operationalizations of uncertainty, we developed a more nuanced theoretical
% understanding of which forms of uncertainty interact in which ways to make social
% learning more or less beneficial compared to asocial learning. 
Detailed theoretical
models and predictions of cultural evolution under uncertainty are critical for
understanding how humans adapt to an uncertain and rapidly changing world, both to
mitigate existential threats~\cite{Moya2020,Jones2021}, and to capitalize on new
opportunities such as transitioning to clean energy use and
production~\cite{NatureEnergyEditorialPromisesPremises2018,Brisbois2022}.

@@

Our model necessarily made some simplifying assumptions that, while
empirically justified in many cases, may not always hold.
\mt{Review the ones mentioned in model section: non-spatial, no within-generation
environmental variability; no horizontal learning}.
We only considered
success-biased learning, although conformity is sometimes the dominant mechanism 
for social influence of behavior well~\cite{Muthukrishna2016a,Smaldino2018b}. 
Another implicit assumption
in our model was that the number of behaviors was constant, as was the relationship
between their payoffs---one was always optimal, and the rest were equally
suboptimal. However, this fails to account for evolutionary feedback which creates
new behavioral affordances as time progresses, e.g.\ via niche 
construction~\cite{Smaldino2012,Heras-Escribano2020} or cumulative cultural
evolution and dynamic network structure~\cite{Smolla2019,Derex2020}. 
Adjusting any of these assumptions and running new computational analyses could
yield further understanding of the evolution of social learning across diverse
contexts.

>>>>

Structure: 
\begin{itemize}
  \item 
    Review
  \item
    Cultural evolutionary considerations/modeling choices reflection/future work
  \item
    Improved individual learning/modeling choices/future work
  \item
    Keep conclusion subsec
\end{itemize}

\mt{Need to make this section more specific in reviewing the findings and 
the key insights and explanations about individual and social payoffs, how
individual learning supports social learning, etc.} By
systematizing four common uncertainty dimensions we developed a model of the
evolution of social learning that predicts how different forms of uncertainty might
interact to foster or suppress social learning.  The model reproduced classic
predictions that social learning can yield higher payoffs than individual learning
when uncertainty is sufficiently limited.  
% By disambiguating and organizing various
% operationalizations of uncertainty, we developed a more nuanced theoretical
% understanding of which forms of uncertainty interact in which ways to make social
% learning more or less beneficial compared to asocial learning. 
Detailed theoretical
models and predictions of cultural evolution under uncertainty are critical for
understanding how humans adapt to an uncertain and rapidly changing world, both to
mitigate existential threats~\cite{Moya2020,Jones2021}, and to capitalize on new
opportunities such as transitioning to clean energy use and
production~\cite{NatureEnergyEditorialPromisesPremises2018,Brisbois2022}.

@@

Our model necessarily made some simplifying assumptions that, while
empirically justified in many cases, may not always hold.
\mt{Review the ones mentioned in model section: non-spatial, no within-generation
environmental variability; no horizontal learning}.
We only considered
success-biased learning, although conformity is sometimes the dominant mechanism 
for social influence of behavior well~\cite{Muthukrishna2016a,Smaldino2018b}. 
Another implicit assumption
in our model was that the number of behaviors was constant, as was the relationship
between their payoffs---one was always optimal, and the rest were equally
suboptimal. However, this fails to account for evolutionary feedback which creates
new behavioral affordances as time progresses, e.g.\ via niche 
construction~\cite{Smaldino2012,Heras-Escribano2020} or cumulative cultural
evolution and dynamic network structure~\cite{Smolla2019,Derex2020}. 
Adjusting these or other assumptions and performing new analyses could
add further nuance to our theoretical understanding of the evolution of social learning.

We hypothesized that individual learning supports social learning. One way to 
test this would be to improve the individual learning algorithm, say with Q-learning(?).
If better individual learning really hedges against outdated social information,
then
